---
title: "COMPSCIX 415.2 Homework 6"
author: "Jateen Bhatt"
date: "7/16/2018"
output: html_document
---

Excercise 1 \newline

Question 1. Age, Smoking and Mortality \newline

Question 2. 1,314 observations on women for the following variables. \newline 

a. survival status after 20 years, a factor with levels Alive Dead \newline

b. smoker status No Yes \newline

c. age in years \newline

Question 3. 
```{r}
library(mosaicData)
library(tidyverse)
Whickham %>% count( smoker , outcome )
```
Here we see 4 outcomes \newline
a) Not smoking and alive b) Not smoking and Dead c) Smoking and Alive d) Smoking and Dead \newline
This doesn't make sense since I'd expect a higher proportion of smokers to be dead. \newline

Question 4.
```{r}
library(mosaicData)
library(tidyverse)
Whickham %>% count( smoker , outcome, age <= 44, ordered=TRUE)
```
```{r}
library(mosaicData)
library(tidyverse)
Whickham %>% count( smoker , outcome, age > 44 | age <= 64)
```
```{r}
library(mosaicData)
library(tidyverse)
Whickham %>% count( smoker , outcome, age >= 65)
```


Excercise 2.
Question 1 and 2
```{r}
library(tidyverse)
n <- 10000

# look at ?rgamma to read about this function
gamma_samp <- tibble(x = rgamma(n, shape = 1, scale = 2)) 
#gamma_samp
ggplot(gamma_samp) + geom_histogram(aes(x = gamma_samp), binwidth = 0.5, fill = "grey", color = "black")
mean_samp <- gamma_samp %>% .[['x']] %>% mean()
mean_samp
```
Question 3
```{r}
library(tidyverse)
n <- 30

# look at ?rgamma to read about this function
gamma_samp <- tibble(x = rgamma(n, shape = 1, scale = 2)) 
#gamma_samp
ggplot(gamma_samp) + geom_histogram(aes(x = gamma_samp), binwidth = 0.5, fill = "grey", color = "black")
mean_samp <- gamma_samp %>% .[['x']] %>% mean()
mean_samp
```

Question 4, Question 5 and Question 6: I was having problems calculating the standard deviation
```{r}
# create a vector with 10000 NAs
mean_samp <- rep(NA, 10000)

# start a loop
for(i in 1:10000) {
  g_samp <- rgamma(30, shape = 1, scale = 2)
  mean_samp[i] <- mean(g_samp)
}
# Convert vector to a tibble
mean_samp <- tibble(mean_samp)
ggplot(mean_samp) + geom_histogram(aes(x = mean_samp), binwidth = 0.5, fill = "grey", color = "black")
mean_sample <- mean_samp %>% .[['NA']] %>% mean()
```

Question 8
```{r}
# create a vector with 10000 NAs
mean_samp <- rep(NA, 300)

# start a loop
for(i in 1:300) {
  g_samp <- rgamma(30, shape = 1, scale = 2)
  mean_samp[i] <- mean(g_samp)
}
# Convert vector to a tibble
mean_samp <- tibble(mean_samp)
ggplot(mean_samp) + geom_histogram(aes(x = mean_samp), binwidth = 0.5, fill = "grey", color = "black")
```
