---
title: "COMPSCIX 415.2 Homework 3"
author: "Jateen Bhatt"
date: "6/26/2018"
output: html_document
---

Section 3.8.1 Excercises
```{r}
library(tidyverse)
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_point()
```

Question 1: Overplotting, this makes it hard to see the overlapping data/ mass of data. 

Question 2: width and height are used to control the amount of vertical and horizontal jitter. 

Question 3. Both can bbe used to overcome ovrerplotting, but with geom_count you can get a more precise number on each plot point (if there is overplotting at that point)

Question 4. --> default position adjustment is for the median of the data to be in the center of the chart. 
```{r}
library(tidyverse)
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) + 
  geom_boxplot()
```


Section 3.9.1 Excercises

Question 2: Actually in the coord_polar documentation there was no right-up on what the labs() refers to. I infured from looking at the example in the homework that it basically tells the geom_bar to reference specific x and y values

Question 4: (a) This chart shows an increasing hwy mileage as per city mileage on most vehicles. 
(b) coord_fixed() defines and sets the aspect ratio of the 2 variables (x and y), in this case the aspect is maintained between the 2 coordinate points
(c) geom_abline() shows, in this example, a diagonal line which basically represent the center of the chart. Useful for annotating the plots

```{r}
library(tidyverse)
ggplot(data = mpg, mapping = aes(x = cty, y = hwy)) +
  geom_point() + 
  geom_abline() +
  coord_fixed()
```

Section 4.4

Question 1 --> actually this worked for me.. I'm assuming that the version of r that I'm using was able to intepret the missing fields and work through it..

Question 2. --> 
```{r}
library(tidyverse)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

ggplot(data = diamonds)
  geom_point(mapping = aes(x = carot, y = price))

filter (mpg, cyl == 8)
filter(diamonds, carat > 3)
```


Section 5.2.4
Question 1
1. filter ---> arrival delays of 2 or more hours
```{r}
library(nycflights13)
filter(flights, arr_delay >=120)
```
2. filter --> flew to houstan (IAH or HOU)
```{r}
library(nycflights13)
filter(flights, dest == 'HOU')
```
3. filter --> were operated by United, American or Delta
```{r}
library(nycflights13)
filter(flights, carrier == 'UA')
filter(flights, carrier == 'AA')
filter(flights, carrier == 'DL')
```
4. filter --> flights departed in summer months 
```{r}
library(nycflights13)
filter(flights, month %in% c(7, 8, 9))
```
5. filter --> arrived 2 hours late but didn't leave late
```{r}
library(nycflights13)
filter(flights, dep_delay == 0 | arr_delay >= 120)
```
6. filter --> departed more than an hour late but made up for 30 minutes in the air
--> I think I got this wrong and need to read more about how to write the string better
```{r}
library(nycflights13)
filter(flights, dep_delay >= 60 | arr_delay <= 30)
```
7. filter --> flights that left between midnight and 6am. I just did a less than 0600 filter. 
```{r}
library(nycflights13)
filter(flights, sched_dep_time <= 0600)
```

Question 2: Between dplyr is useful in selecting a range of values in a table.

Section 5.4.1

Question 1. I'm going to say that if you square 5 to the 5th power, that gives you the number of ways you can sort all 5 fields using the select command. 

Question 3. One_of() seems to help in detecting outliers or vectors that are unique 