---
title: "COMPSCIX 415.2 Homework 5/Midterm"
author: "Jateen Bhatt"
date: "7/10/2018"
output: html_document
---
--> RStudio and R Markdown (3 points)
Use markdown headers in your document to clearly separate each midterm question and add a table of contents to your document.


The tidyverse packages (3 points) \newline

By now you’ve used at least five different packages from the tidyverse for plotting, data munging, reshaping data, importing/exporting data, and using tibbles (the tibble package is used for this without you even realizing it’s there). \newline


Can you name which package is associated with each task below? \newline

Plotting - ggplot2 \newline

Data munging/wrangling - dplyr \newline

Reshaping (speading and gathering ) data - tidyr \newline

Importing/exporting data - readr \newline


Now can you name two functions that you’ve used from each package that you listed above for these tasks? \newline

Plotting - from ggplot2 --> coord_flip, geom_dotplot \newline

Data munging/wrangling - mutate, sample_n (actually this was covered in week 6 class) \newline

Reshaping data - from tidyr --> spread, seperate \newline

Importing/exporting data - from readr --> read_csv, write_csv \newline


R Basics (1.5 points)
Fix this code with the fewest number of changes possible so it works: \newline
My_data.name___is.too00ooLong! <- c( 1 , 2   , 3 )

```{r}
"My_data.name___is.too00ooLong!" <- c( 1 , 2   , 3 )
```

Fix this code so it works:
my_string <- C('has', 'an', 'error', 'in', 'it)
```{r}
my_string <- c('has', 'an', 'error', 'in', 'it')
my_string
```

Look at the code below and comment on what happened to the values in the vector. \newline

my_vector <- c(1, 2, '3', '4', 5) \newline

my_vector 
## [1] "1" "2" "3" "4" "5" 

A list of charecters are generated, the numbers which should be treated as integers are instead characters. 

Data import/export (3 points)
Download the rail_trail.txt file from Canvas (in the Midterm Exam section) and successfully import it into R. Prove that it was imported successfully by including your import code and taking a glimpse of the result.
```{r}
rail_trail = read.csv("/Users/jbhatt/Downloads/rail_trail.txt")
rail_trail[1:4,]
```

Export the file into a comma-separated file and name it “rail_trail.csv”. Make sure you define the path correctly so that you know where it gets saved. Then reload the file. Include your export and import code and take another glimpse.
```{r}
write.csv(rail_trail, file = "/Users/jbhatt/Documents/rail_trail.txt")
```


Visualization (6 points)
Critique this graphic: give only three examples of what is wrong with this graphic. Be concise. \newline

This graph has 3 issues that I can see. \newline

1. It is very difficult to understand scale with closely matching numerical values. \newline

2. The under 45 age range should be further devided or does not match the scale of the other age ranges. \newline

3. The bubbles don't neccassary represent a scale out of 100%. It would also help if we can see the gender breakdown between ages. \newline


Reproduce this graphic using the diamonds data set.

```{r}
library(tidyverse)
ggplot(data = diamonds, mapping = aes(x = cut, y = carat, color = color)) + 
  geom_boxplot() +
  coord_flip()
```



The previous graphic is not very useful. We can make it much more useful by changing one thing about it. Make the change and plot it again. \newline

I made the changes above.. As you can see you can compare different colors side by side by cut. \newline

Data munging and wrangling (6 points)
Is this data “tidy”? If yes, leave it alone and go to the next problem. If no, make it tidy. Note: this data set is called table2 and is available in the tidyverse package. It should be ready for you to use after you’ve loaded the tidyverse package.
table2
country
<chr>
year
<int>
type
<chr>
count
<int>
Afghanistan	1999	cases	745
Afghanistan	1999	population	19987071
Afghanistan	2000	cases	2666
Afghanistan	2000	population	20595360
Brazil	1999	cases	37737
Brazil	1999	population	172006362
Brazil	2000	cases	80488
Brazil	2000	population	174504898
China	1999	cases	212258
China	1999	population	1272915272
1-10 of 12 rows

Yes, this data frame is tidy. \newline

Create a new column in the diamonds data set called price_per_carat that shows the price of each diamond per carat (hint: divide). Only show me the code, not the output. \newline
```{r}
library(tidyverse)
diamonds$price_per_carat <- diamonds$price / diamonds$carat
#diamonds$price_per_carat
```

For each cut of diamond in the diamonds data set, how many diamonds, and what proportion, have a price > 10000 and a carat < 1.5? There are several ways to get to an answer, but your solution must use the data wrangling verbs from the tidyverse in order to get credit.
```{r}
library(tidyverse)
filter(diamonds, price > 10000 & carat > 1.5)
```

Do the results make sense? Why?
Do we need to be wary of any of these numbers? Why? \newline
No, there is no relationship between the price_per carat and the cut type. This would make sense if we understood the types of diamonds that were in demand. But based on the data above we don't know that. \newline

EDA (6 points)
Take a look at the txhousing data set that is included with the ggplot2 package and answer these questions:

During what time period is this data from? 2000 - 2016 (16 years) \newline

How many cities are represented? 46 \newline

Which city, month and year had the highest number of sales? Houstan \newline

What kind of relationship do you think exists between the number of listings and the number of sales? Check your assumption and show your work.
I believe the size of the city field is missing. Some cities may have more land available for housing development, which might affect the volume and inventory numbers. \newline

What proportion of sales is missing for each city?
Population of City \newline

Looking at only the cities and months with greater than 500 sales:
```{r}
library(tidyverse)
filter(txhousing, sales > 500)
```

Are the distributions of the median sales price (column name median), when grouped by city, different? The same? Show your work.
They are different \newline

Why might we want to filter out all cities and months with sales less than 500?
We might get an idea of exclusive neibhorhoods or maybe even any kind of housing discrimination.\newline

Git and Github (1.5 points)
To demonstrate your use of git and Github, at the top of your document put a hyperlink to your Github repository.

Once you are finished with your midterm, commit your final changes with the comment “finished the midterm - woohoo” and push your R Markdown file and your html or pdf file to Github.